Development of a Reinforcement Learning Enabled Cattle Tracker Prototype

### 2025-02-12 paper/main.tex
Update main.tex

\section{Using Overleaf}

If you are reading this you have already downloaded the zip file with the template (\textbf{CANAI \conferenceyear\xspace LaTex Template.zip}). All you need to do is to upload it into Overleaf:

\begin{enumerate}
\item Go to \url{overleaf.com}.
\item Click on new project (top left menu).
\item Choose the \textbf{upload project} option.
\item Upload the \textbf{zip file} to Overleaf.
\end{enumerate}

>>>>

The developed reinforcement learning-enabled cattle tracker prototype was successfully assembled and tested. The prototype consists of key components such as a solar panel, battery, communication module, and processing unit, as shown in Figure~\ref{fig:prototype}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\textwidth]{./figs/prototype.png}
  \caption{Prototype of the reinforcement learning-enabled cattle tracker. The device consists of a solar panel for power harvesting, a rechargeable battery, and an embedded microcontroller for decision-making and communication.}
  \label{fig:prototype}
\end{figure}

The system was evaluated based on its power consumption, data transmission efficiency, and overall performance in real-world conditions. The reinforcement learning algorithm optimized the power usage by balancing data collection, storage, and transmission to ensure continuous operation.

Additionally, the power levels of the device over time were analyzed to assess energy efficiency. Figure~\ref{fig:power_levels} shows the variation in power consumption during different operational phases.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{./figs/power_levels.png}
    \caption{Power consumption levels of the cattle tracker over time. Different colors represent different operational phases such as data transmission, storage, and idle states.}
    \label{fig:power_levels}
\end{figure}

\section{Conclusion}
